Fishing for Spam

### 2024-08-08 products/manuscript/Manuscript.qmd
Final commit

---
title: "Fishing for Spam"
author: Sean O'Sullivan
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
nocite: |
  @*
execute:
  echo: false
---

@@

```{r}
cm.df <- readRDS(here("results", "tables", "confusion-matrix-compared.rds"))
cm.df
```

>>>>

---
title: "Fishing for Spam"
author: Sean O'Sullivan
format:
  docx:
    df-print: kable
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
nocite: |
  @*
execute:
  echo: false
---

@@

```{r}
cm.df <- readRDS(here("results", "tables", "confusion-matrix-compared.rds"))
cm.df %>% select(Model, F1, Recall, Precision, `Balanced Accuracy`)
```
